Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/design.tex
design (section 4.0) nits

\item Using the grammar to define both the \emph{external format} and the \emph{internal
    representation}, allowing the same grammar to be re-used in multiple programs, avoiding
  vulnerabilities like the Android Master Key.

\item Both parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions. This prevents
      vulnerabilities such as the XNU bug, where format recognition and semantics
      are mixed and interact in unexpected ways.

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to provide programmers
      a consistent, unambiguous view of the data,
      to avoid bugs such as in the Python ZIP library.

\item Allow programmers to define grammars for complex real-world
      data formats through well-defined extensibility mechanisms.

>>>>

\item Using a single grammar to define both the \emph{external format} and the
  \emph{internal representation}.  This allows the same grammar to be re-used
  in multiple programs, and helps avoid vulnerabilities like the Android Master
  Key bug.

\item Parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions. This prevents
      vulnerabilities such as the iOS XNU bug, where format recognition and semantics
      are mixed and interact in unexpected ways.

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to provide programmers
      a consistent, unambiguous view of the data.
      This helps avoid bugs such as the one discovered in the
      Python ZIP library~\cite{python-bug:20078}.

\item Allow programmers to define grammars for complex real-world
      data formats through well-defined extensibility mechanisms. 
      This helps prevent programmers from falling back on manual
      parsing when encountering a complex data format.
